Detecting Facial Expressions in Professional Tennis Matches

### 2017-07-28 Report06-12.Rmd
typo

```{r ShotangleCompare, eval=FALSE, fig.cap:".\\label{fig:ShotangleCompare}"}
CompShot <- ALLmetaIMGnamedFaces %>% 
  filter(shotangle=="Player Shoulder Height", 
         bg=="Logo wall", 
         situation=="Court player close−up",
         type=="Google" | type=="Manual",
         player2=="AMurray", player2:"AMurray")

>>>>

```{r ShotangleCompare, eval=FALSE, fig.cap=".\\label{fig:ShotangleCompare}"}
CompShot <- ALLmetaIMGnamedFaces %>% 
  filter(shotangle=="Player Shoulder Height", 
         bg=="Logo wall", 
         situation=="Court player close−up",
         type=="Google" | type=="Manual",
         player2=="AMurray", player2:"AMurray")
